Numerical Stability of Detonations in White Dwarf Simulations

### 2018-11-22 papers/ignition/paper.tex
Describe stopping criterion

>>>>

The simulation is terminated when the peak temperature on the domain first reaches
$4 \times 10^9$ K, which we call a thermonuclear ignition. This stopping criterion is a
proxy for the beginning of a detonation. Reaching this temperature does not guarantee
that a detonation will begin, and in this study we do not directly address the question
of whether a ignition of this kind always leads to a detonation. Rather, the main question
we investigate here is whether this ignition is numerically converged. A converged ignition
is a prerequisite to having a converged detonation.
